---
title: "Docking Hands-on BIMM 143 2_15"
output: html_notebook
---

Download and prep HIV-1  PR structure '1hsg'. This creates file in the working dir
```{r}
library(bio3d)
file.name<-get.pdb('1hsg')
hiv<-read.pdb(file.name)
```

Prep initial protein and ligand input files
```{r}
prot <- trim.pdb(hiv, 'protein')
lig <- trim.pdb(hiv, 'ligand')

write.pdb(prot, file = '1hsg_protein.pdb')
write.pdb(lig, '1hsg_ligand.pdb')
```
Now, launch AutoDock Tools (ADT)
On ADT: File > Read

*Note that on ADT you have to type in save file path or drag and drop. Save to this project folder.

##Prepare a docking config file
On a .txt file enter calculations for docking.
In terminal run Vina with input dockconfig.txt,
specify to record output in log.txt

(example file: dockconfig.txt)
1hsg ADT specs:
Spacing: 1
Coord: (16, 25, 4) obtained from ADT Grid box tool
Dim: (30, 30, 30) obtained from ADT Grid box tool

##Dock Ligand
Terminal input:
~/Downloads/autodock_vina_1_1_2_mac/bin/vina --config dockconfig.txt --log log.txt

**Download docking software at:**
http://vina.scripps.edu/download.html
We will run it from Terminal/Cmd Line
*A fast docking program that requires minimal user intervention and is often employed for HT cirtual screening.*

##Analyze Docking Results on VMD
```{r}
library(bio3d)
res <- read.pdb('all.pdbqt', multi = TRUE)
write.pdb(res, 'results.pdb')
```
Open VMD and load results.pdb and hsg_protein.pdb
play around to create an understandable representation.
Then you can press play on VMD Main to see how ADT attempted different dockings.

Compare original ligand with added H using rmsd()
```{r}
res<- read.pdb('all.pdbqt', multi = TRUE)
ori <- read.pdb('hsg_ligand.pdbqt')
rmsd(ori,res)
```


